Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

We investigate possible variations in the dynamics of the molecular structures of \flower 
by adopting different sets of $n_{\rm cut}$ % in identifying the MCCs
to test the robustness of our results against the choice of density threshold. 
That is, how sensitive are the structure properties, and thus, the 
results presented in \Sec{singless} dependent on the choice of density thresholds.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
are limited by the spatial resolution. 
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion 
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges in $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

% different evolutionary stages
We do not find any major quantitative differences in the MCCs of \flower between its accreting and starburst phase with respect to those observed in the nearby Universe (see \Fig{larsons_single}), which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.

>>>>

We investigate possible variations in the dynamics of the molecular structures of \flower
by adopting different
%mm2 sets
    values
of $n_{\rm cut}$ % in identifying the MCCs
to test the robustness of our results against the choice of density threshold.
That is, how sensitively are the structure properties, and thus, the
results presented in \Sec{singless}, dependent on the choice of density thresholds?

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
However, the sizes of MCCs are almost a factor of two smaller. This
%mm2 likely suggest
    suggests
that the sizes of \highz molecular gas structures reported in the literature
are
%mm2
   probably
limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.

   The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in those are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs
%mm2 of \flower
are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

% different evolutionary stages
%mm2 [rearranged]
We do not find any major quantitative differences  (see \Fig{larsons_single}) in the MCCs of \flower with respect to those observed in the nearby Universe between its accreting and starburst phase, which are separated by $\simeq$300\,Myr. However, MCCs in the \SB phase have lower $\alpha_{\rm vir}$ compared to the accreting phase. This is expected for \SF to proceed.
